Figures

### 2018-05-11 scripts/analysis.Rmd
add nws area plots
fix figure sizes, label abbrevations, panel labels
update fig and table captions from gdoc

```{r lake_characteristics_table, echo=FALSE, results='asis'}

@@

```{r fig.cap="Diagram showing the inter-lake watershed (IWS) and network watershed (NWS) of three lakes. Here the IWS of lake 3 encompasses the IWS of lake 2 because of its small size but not the IWS of lake 1 because it is large.  In contrast, the NWS of lake 3 extends to the headwaters of the lake chain.", echo=FALSE}
knitr::include_graphics("../figures/iws_nws.pdf")
```

@@

```{r global_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from global model posterior relative to NES data.", warning=FALSE, fig.width = 3.5, fig.height = 3.2}

@@

```{r partition_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from hierarchical model posteriors relative to NES data. Lighter colored lines and lighter colored polygons represent the estimates from the lower of the two partition groups (see Table 2).", fig.width = 4.8, fig.height=5, warning=FALSE}

@@

```{r k_viz, echo=FALSE, message=FALSE, fig.cap="Distribution of Vollenweider's k in low and high connectivity partitions at the IWS and NWS scales. Lighter colors indicate the lower of the two partition groups (see Table 2).", fig.width=5, fig.height=3.8, warning=FALSE}

@@

```{r maps, echo=FALSE, fig.cap="Map of lake connectivity partitions where lighter colored lakes have metric values on the lower side of their respective partitions (see Table 2).", warning=FALSE, message=FALSE}

@@

>>>>

```{r lake_characteristics_table, echo=FALSE, results='asis', message=FALSE, warning=FALSE}

@@

```{r fig.cap="Diagram showing the inter-lake watershed (IWS) and network watershed (NWS) of three lakes. Here the IWS of lake 3 encompasses the IWS of lake 2 because of it is smaller than 10 ha small size but it does not encompass the IWS of lake 1 because it has an area of at least 10 ha. In contrast to the IWS boundaries, the NWS boundaries extend to the headwaters of the lake chain.", echo=FALSE}
knitr::include_graphics("../figures/iws_nws.pdf")
```

@@

```{r global_vollenweider_viz, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and the global model fit to the data as the median and central 95% interval estimates.", warning=FALSE, fig.width = 3.5, fig.height = 3.2}

@@

```{r partition_vollenweider_viz, echo=FALSE, fig.cap="Residence time (yr) versus P retention (%) for the NES dataset and hierarchical model fits to the data as the median and central 95% interval estimates.  The green lines and symbols are the estimates from the lower of the two partition groups while the purple lines are estimates for the upper of the two partition groups (see Table 2).", fig.width = 4.8, fig.height=5, warning=FALSE}

@@

```{r k_viz, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from the Vollenweider's equation in low and high connectivity partitions at the (A) IWS and (B) NWS scales. Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", fig.width=5, fig.height=3.8, warning=FALSE}

@@

```{r maps, echo=FALSE, fig.cap="Maps showing the locations of lake connectivity partitions. Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", warning=FALSE, message=FALSE}

@@

```{r graphical_exploratory_analysis_cont_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6.3, fig.cap="Exploratory plots cont x 2"}
